Using hydraulic geometry and the SWOT satellite to remotely sense river gas exchange velocity

### 2022-01-24 scraps.Rmd
manuscript v7

>>>>

Figure 7a evaluates the $FCO_2$ estimates using the same 4 error metrics as Figure 5a. BIKER, the sole remote technique, is in red while the three in situ techniques are plotted as different shades of purple. We see that BIKER performs slightly worse than all three in situ methods across all metrics except *r*, where it performs similarly (median BIKER *KGE* of `r round(median(results_fco2_rivs[results_fco2_rivs$key == 'FCO2_BIKER',]$KGE),2)` and median *r* of `r round(median(results_fco2_rivs[results_fco2_rivs$key == 'FCO2_BIKER',]$r),2)`). BIKER is also more biased (median *rBIAS* of `r round(median(results_fco2_rivs[results_fco2_rivs$key == 'FCO2_BIKER',]$rBIAS),2)`) than either 'Brinkerhoff 2019' or 'Raymond 2012' models and similarly biased to the 'Raymond 2013' model (median *rBIAS* of `r round(median(results_fco2_rivs[results_fco2_rivs$key == 'FCO2_brinkerhoff2019',]$rBIAS),2)`, `r round(median(results_fco2_rivs[results_fco2_rivs$key == 'FCO2_raymond2012',]$rBIAS),2)`, `r round(median(results_fco2_rivs[results_fco2_rivs$key == 'FCO2_raymond2013',]$rBIAS),2)`, respectively).
